A dispatch-based approach to fully allocate costs in optimal power systems

### 2020-09-08 paper/flow_based.tex
add new figure to paper, adjust legend in subsidy plot

\begin{figure*}
    \includegraphics[width=\linewidth]{de50bf/capex_duration_curve}
    \caption{Duration curve of the CAPEX allocation for production and storage technologies. Hours are sorted such that the total amount of allocated expenditure per hour decreases. With 2.7 bn~\euro\, the first value pushes investments extraordinary high. It is dominated by CAPEX for OCGT to which 92\% of the payments are allocated. This hour alone occasions about the half of all OCGT CAPEX. The following 7000 time-steps are dominated by revenues for onshore wind and reveal a rather even distribution. In hours of low CAPEX allocation (after the second drop) spendings for OCGT start to increase again. These  }
    \label{fig:capex_duration}
\end{figure*}

>>>>

\begin{figure*}
    \includegraphics[width=\linewidth]{de50bf/capex_duration_curve}
    \caption{Duration curve of the CAPEX allocation for production and storage technologies. Hours are sorted such that the total amount of allocated expenditure per hour decreases. With 2.7 bn~\euro\, the first value pushes investments extraordinary high. Due to low renewable potentials, it is dominated by CAPEX for OCGT, to which 92\% of the payments are allocated. This hour alone occasions about the half of all OCGT CAPEX. \Cref{capex_duration} gives a detailed picture of the operational state at this time-step. The following 7000 time-steps are dominated by revenues for onshore wind and reveal a rather even distribution. In hours of low CAPEX allocation (after the second drop) spendings for OCGT start to increase again. These time-steps however play a minor role.}
    \label{fig:capex_duration}
\end{figure*}

\begin{figure}
    \includegraphics[width=\linewidth]{de50bf/operation_high_expenditure}
    \caption{Production, flow and consumption in the system at the hour with the highest expenditures. The size of the circles are proportional to the power production at a node. Size of arrows are proportional to the flow on the transmission line. The depicted hour corresponds to the first value in the duration curve in \cref{fig:capex_duration}.}
    \label{fig:operation_high_expenditure}
\end{figure}
